Towards Contract Modules for the Tezos Blockchain

### 2021-05-17 papers/contract-modules/fmbc2021/fmbc-main.tex
Update fmbc-main.tex
first few sections

\author{Thi Thu Ha Doan}{University of Freiburg, Germany}{doanha@cs.uni-freiburg.de}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

\author{Peter Thiemann}{University of Freiburg, Germany}{thiemann@acm.org}{[orcid]}{[funding]}

@@

\Copyright{Ha Doan and Peter Thiemann} %TODO mandatory, please use full first names. OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

@@

\acknowledgements{I want to thank \dots}%optional

@@

>>>>

\author{Thi Thu Ha Doan}{University of Freiburg,
  Germany}{doanha@cs.uni-freiburg.de}{https://orcid.org/0000-0002-1825-0097}{supported
by a grant from the Tezos foundation}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

\author{Peter Thiemann}{University of Freiburg, Germany}{thiemann@acm.org}{https://orcid.org/0000-0002-9000-1239}{}

@@

\Copyright{Thi Thu Ha Doan and Peter Thiemann} %TODO mandatory, please use full first names. OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

%\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}}
%%TODO mandatory: Please choose ACM 2012 classifications from
%%https://dl.acm.org/ccs/ccs_flat.cfm
\ccsdesc[100]{}

\keywords{contract API, modules, static checking} %TODO mandatory; please add comma-separated list of keywords

@@

% \acknowledgements{I want to thank \dots}%optional

@@

Contracts on the blockchain rarely run in isolation. To be useful
beyond shuffling tokens between user accounts, they need to interact
with the outside world. On the other hand, the outside world also
needs to interact by initiating transactions and starting contracts
that feed information into the blockchain. One direction is addressed
by oracles that watch certain events on the blockchain, create a
response by calculation or gathering data, and then invoke a callback
contract to inject this response into the chain. Trust is an essential
aspect for an oracle.

The other direction is about automatizing certain processes in
connection with the blockchain. For example, opening or closing an
auction according to a schedule, programming a strategy for an
auction, or creating an NFT. To this end, an interface is needed to
invoke contracts safely. Existing interfaces are lacking because they
are essentially untyped (string-based or JSON-based) and often low
level because they require dealing directly with RPC interfaces. Trust
is not needed because the process runs on behalf of a certain user.

Contract modules provide a clean, language-integrated way to interact
with a blockchain. They abstract over underlying string-based
interfaces and details like fee handling. They provide a high-level
typed interface which reduces a contract invocation to a function call
in the language.

Contract modules do not provide a fixed API, but
rather generate a specialized interface for each contract. This
interface is statically checked against the contract implementation to
ensure type safety and exception safety (every failure condition
arising is handled by proper error reporting).

Our work is situated in the context of the Tezos blockchain, which
supports Michelson as its low-level contract language, and the
language OCaml, which supports a powerful module concept that we
enhance with contract modules.

\section{Context}
\label{sec:context}

Tezos is a third generation, account-based, self amendable
blockchain \cite{tezos-whitepaper}. It employs a proof-of-stake consensus protocol, which
includes ways to evolve the protocol itself. The consensus protocol is
executed by so-called bakers and their proposed blocks are checked by
validators. They receive some compensation in the form of
tokens (Tezzies) for their work.

Each Tezos contract owns an account as well as some storage. Contracts
are pure functions of type parameter $\times$ storage $\to$ operation
list $\times$ storage. When a contract is invoked with a parameter,
the blockchain provides the current storage and updates it with the
second, storage component of its return value. The first component is
a list of blockchain operations (contract deployments, token
transfers, contract invocations) that are executed transactionally
after the first invocation terminates. Each invocation may be
accompanied with an amount of tokens that are added to the current
account balance of the contract.

Contracts are implemented in the Michelson language, a fully typed
stack-based language. Each contract has fixed types for its parameter
and for its storage. The storage is initialized when the contract is
deployed. Besides primitive types like unit, int, bool, address, and string,
there are pairs, sums, functions, lists, and maps (and many more) that
can serve as types for storage and parameters.

\section{An auction contract}
\label{sec:an-auction-contract}

As a concrete example, we consider an auction contract. 
\begin{lstlisting}[language=michelson,numbers=none,emph={close,bid},emphstyle=\underbar]
parameter (or (unit %close) (unit %bid));
storage (pair bool          # bidding allowed
         (pair address      #  contract owner
          address           # highest bidder's address
        ));
\end{lstlisting}
This contract has two entrypoints, \lstinline/close/ and \lstinline/bid/,
expressed by giving the single parameter a sum type. To call the
entrypoint \lstinline/close/ we use the parameter \lstinline/Left ()/
otherwise we use \lstinline/Right ()/, where \lstinline/()/ is the sole
value of type \lstinline/unit/. Its storage is a nested pair which
contains a boolean flag and two addresses.
